---
title: "P8105_hw1_hc3212"
author: "HeningCui"
date: "2021/9/26"
output: github_document
---

This is the solution for Homework 1.

## Problem 1 

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

Solution:

Create the sample:

```{r create_df}
library(tidyverse) 
set.seed(1)
prob1_df =
  tibble(
    sample_1 = rnorm(10),
    samp_vec_0 = sample_1 > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g","h", "i", "j"),
    fact_vec = factor(c("low", "high", "low", "high", "low", "high", "low", "mid", "mid", "low"))
  )
```

Taking the mean of each variable.

```{r takemean_pull_var, echo = FALSE}
mean(pull(prob1_df, sample_1))
mean(pull(prob1_df, samp_vec_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, fact_vec))
```

The number and logical vector could take mean while the character and factor vector could not.

Convert the logical, character, and factor variable into numeric.

```{r convert_var, results = 'hide'}
as.numeric(pull(prob1_df, samp_vec_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, fact_vec))
```

Calculate the mean again after convert.

```{r recalculate_mean, echo = FALSE}
mean(as.numeric(pull(prob1_df, samp_vec_0)))
mean(as.numeric(pull(prob1_df, char_vec)))
mean(as.numeric(pull(prob1_df, fact_vec)))
```

After covert, the factor and logical variable could turn into numeric while the character variable could not. The logical variable with "TRUE" and "FALSE" result could turn into "1" and "0", then the mean could be calculated. the facter variable could turn into "1", "2", "3", and calculated mean. Character variable will all equal to NA, the mean will return as NA.
 
## Problem 2
The trunk below is to download the a package containing the penguins dataset:

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

The **Penguins** dataset contains the following variables: `r ls(penguins)`.

Bill depth (mm) is a `r class(pull(penguins, bill_depth_mm))` variable. The mean of bill depth (mm) is `r mean(pull(penguins, bill_depth_mm), na.rm=TRUE)`. Values for bill depth range from `r range(pull(penguins, bill_depth_mm), na.rm=TRUE)` (min, max).

Bill length (mm) is a `r class(pull(penguins, bill_length_mm))` variable. The mean of bill length (mm) is `r mean(pull(penguins, bill_length_mm), na.rm=TRUE)`. Values for bill length range from `r range(pull(penguins, bill_length_mm), na.rm=TRUE)` (min, max). 

Body mass (g) is a `r class(pull(penguins, body_mass_g))` variable. The mean of Body mass (g) is `r mean(pull(penguins, body_mass_g), na.rm=TRUE)`. Values for bill depth range from `r range(pull(penguins, body_mass_g), na.rm=TRUE)` (min, max). 

Flipper length (mm) is a `r class(pull(penguins, flipper_length_mm))` variable. The mean of flipper length (mm) is `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)`. Values for flipper length range from `r range(pull(penguins, flipper_length_mm), na.rm=TRUE)` (min, max).

Island is a `r class(pull(penguins, island))` variable, which has `r levels(pull(penguins, island))` islands.
	
Sex is a `r class(pull(penguins, sex))` variable, which has `r levels(pull(penguins, sex))` categories.
	
Species is a `r class(pull(penguins, species))` variable, which has species `r levels(pull(penguins, species))`.
	
Year is a `r class(pull(penguins, year))` variable. The range for the years variable is from `r range(pull(penguins, year))`.
	
The number of rows (observations) in the Penguin dataset is `r nrow(penguins)`.
	
The number of columns (variables) in the Penguin dataset is `r ncol(penguins)`.
	
This chunk is to generate a scatter plot for bill length and flipper length, each color represents a different species.

```{r scatterplot_penguin}
library(ggplot2)
set.seed(1)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + ggtitle("Flipper Length vs. Bill Length for Penguins by Species") + theme(plot.title = element_text(hjust = 0.6))

ggsave("scatterplot_penguin.pdf")
```

