---
title: "P8105_hw1_hc3212"
author: "HeningCui"
date: "2021/9/26"
output: github_document
---

This is the solution for Homework 1.
```{r library, results = 'hide'}
library(tidyverse)
```

## Problem 1 

Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r create_df, echo = FALSE}
prob1_df =
  tibble(
    sample_1 = rnorm(10),
    samp_vec_0 = sample_1 > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g","h", "i", "j"),
    fact_vec = factor(c("low", "high", "low", "high", "low", "high", "low", "mid", "mid", "low"))
  )
prob1_df
```

Taking the mean of each variable.
```{r takemean_pull_var, echo = FALSE}
mean(pull(prob1_df, sample_1))
mean(pull(prob1_df, samp_vec_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, fact_vec))
```

The number and logical vector could take mean while the character and factor vector could not.

Convert the logical, character, and factor variable into numeric.
```{r convert_var, results = 'hide'}
as.numeric(pull(prob1_df, samp_vec_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, fact_vec))
```
```{r}
prob1_df
```
